Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2021-04-13 ms/main.tex
Fix bib style
Fixes around line 61

Cooperative behavior can be subject to \emph{cultural transmission}, which allows an individual to acquire attitudes or behavioral traits from other individuals in its social group through imitation, learning, or other modes of communication \citep{cavalli1981cultural,richerson2008not}.
\citet{feldman1985gene} introduced the first model for the evolution of altruism by cultural transmission with kin selection and demonstrated that if the fidelity of cultural transmission of altruism is $\varphi$, then the condition for evolution of altruism in the case of sib-to-sib altruism is \citep[Eq.~16]{feldman1985gene}
\begin{equation} \label{eq:feldman1985}
c < b \cdot \varphi - \frac{1-\varphi}{\varphi} \,.
\end{equation}
In inequality~\ref{eq:feldman1985}, $\varphi$ takes the role of relatedness ($r$ in inequality~\ref{eq:hamilton_rule}) or assortment ($m$ in inequality~\ref{eq:eshel1982}), but the effective benefit $b\cdot \varphi$ is  reduced by $(1-\varphi)/\varphi$.
This shows that under a cultural transmission, the condition for the evolutionary success of altruism entails a modification of Hamilton's rule (inequality~\ref{eq:hamilton_rule}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Bibliography
\bibliographystyle{rsnat}
\bibliography{bib}

>>>>

Cooperative behavior can be subject to \emph{cultural transmission}, which allows an individual to acquire attitudes or behavioral traits from other individuals in its social group through imitation, learning, or other modes of communication \citep{cavalli1981cultural,richerson2008not}.
\citet{feldman1985gene} introduced the first model for the evolution of altruism by cultural transmission with kin selection and demonstrated that if the fidelity of cultural transmission of altruism is $\varphi$, then the condition for evolution of altruism in the case of sib-to-sib altruism is \citep[Eq.~16]{feldman1985gene}
\begin{equation} \label{eq:feldman1985}
c < b \cdot \varphi - \frac{1-\varphi}{\varphi} \,.
\end{equation}
In inequality~\ref{eq:feldman1985}, $\varphi$ replaces relatedness ($r$ in inequality~\ref{eq:hamilton_rule}) or assortment ($m$ in inequality~\ref{eq:eshel1982}), but the effective benefit $b\cdot \varphi$ is  reduced by $(1-\varphi)/\varphi$.
This shows that under a cultural transmission, the condition for the evolutionary success of altruism entails a modification of Hamilton's rule (inequality~\ref{eq:hamilton_rule}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Bibliography
\bibliographystyle{unsrtnat}
\bibliography{bib}
